Learning the local coding scheme: Jointly Optimized Locally Linear Classifiers

### 2017-09-12 paper/LLSVM_AAAI18/LLSVM-nostd.tex
done for aaai18

			phishing              & Train loss & Test loss & Acc(\%) &Test time \\
			\textbf{SVM} 		   	&0.1826$\pm$0.0002  &0.1964$\pm$0.0006  & 92.24 $\pm$ 0.10 & $\times$1  \\ \hline
			\textbf{LLSVM}     		&0.1688$\pm$0.0027  &0.1861$\pm$0.0042  & 92.66 $\pm$ 0.23 & $\times$8.91 \\ \hline
			\textbf{LLC-SAPL}       &0.1385$\pm$0.0011  &0.1509$\pm$0.0026  & 93.92 $\pm$ 0.18 & $\times$9.27 \\ \hline
			\textbf{LLC-JO}         &0.0580$\pm$0.0016  &0.1026$\pm$0.0026  & 95.66 $\pm$ 0.17 & $\times$8.66 \\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0487$\pm$0.0020}  &\textbf{0.0965$\pm$0.0040}  & \textbf{95.84 $\pm$ 0.34} &$\times$8.91 \\ \hline
			Magic04              & Train loss & Test loss & Acc(\%) &Test time \\
			\textbf{SVM} 		   	&0.4810$\pm$0.0002  &0.5004$\pm$0.0014  &78.33 $\pm$ 0.13  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4022$\pm$0.0018  &0.4289$\pm$0.0016  &79.57 $\pm$ 0.30  &$\times$21.56 \\ \hline
			\textbf{LLC-SAPL}       &0.3670$\pm$0.0019  &0.3923$\pm$0.0031  &81.60 $\pm$ 0.18  &$\times$22.04 \\ \hline
			\textbf{LLC-JO}         &0.3025$\pm$0.0010  &0.3339$\pm$0.0017  &84.88 $\pm$ 0.36  &$\times$22.92\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.2852$\pm$0.0008}  &\textbf{0.3238$\pm$0.0029}  &\textbf{85.14 $\pm$ 0.44}   &$\times$22.92\\ \hline
			IJCNN              & Train loss & Test loss & Acc(\%) &Test time\\
			\textbf{SVM} 		   	&0.1827$\pm$0.0000  &0.1863$\pm$0.0000  & 90.50 $\pm$ 0.00  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.1081$\pm$0.0028  &0.1130$\pm$0.0039  & 94.51 $\pm$ 0.30  &$\times$15.52\\ \hline
			\textbf{LLC-SAPL}       &0.1002$\pm$0.0017  &0.1054$\pm$0.0015  & 95.17 $\pm$ 0.21  &$\times$15.78\\ \hline
			\textbf{LLC-JO}         &0.0703$\pm$0.0002  &0.0683$\pm$0.0024  & 97.66 $\pm$ 0.11  &$\times$16.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0550$\pm$0.0007}  &\textbf{0.0584$\pm$0.0018}  &\textbf{98.26 $\pm$ 0.12}   &$\times$15.42\\ \hline
			w8a              & Train loss & Test loss & Acc(\%) &Test time\\
			\textbf{SVM} 		   	&0.0552$\pm$0.0001  &0.0567$\pm$0.0003  & 97.07 $\pm$ 0.00  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.0320$\pm$0.0014  &0.0333$\pm$0.0019  & 98.45 $\pm$ 0.25  &$\times$11.72\\ \hline
			\textbf{LLC-SAPL}       &0.0262$\pm$0.0007  &0.0274$\pm$0.0005  & 98.74 $\pm$ 0.18  &$\times$12.78\\ \hline
			\textbf{LLC-JO}         &0.0250$\pm$0.0003  &0.0262$\pm$0.0004  & 98.74 $\pm$ 0.07  &$\times$10.01\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0213$\pm$0.0016}  &\textbf{0.0228$\pm$0.0028}  &\textbf{98.96 $\pm$ 0.31}   &$\times$10.28\\ \hline
			connect-4              & Train loss & Test loss & Acc(\%) &Test time\\
			\textbf{SVM} 		   	&0.4268$\pm$0.0002  &0.4257$\pm$0.0008  & 81.50 $\pm$ 0.12  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.2998$\pm$0.0017  &0.3196$\pm$0.0021  & 87.30 $\pm$ 0.25  &$\times$7.52\\ \hline
			\textbf{LLC-SAPL}       &0.2626$\pm$0.0007  &0.2901$\pm$0.0013  & 88.19 $\pm$ 0.15  &$\times$8.78\\ \hline
			\textbf{LLC-JO}         &0.2180$\pm$0.0025  &0.2663$\pm$0.0030  & 89.15 $\pm$ 0.23  &$\times$9.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.1496$\pm$0.0017}  &\textbf{0.2225$\pm$0.0020}  &\textbf{90.94 $\pm$ 0.21}   &$\times$9.92\\ \hline
			Covtype              & Train loss & Test loss & Acc(\%) &Test time\\
			\textbf{SVM} 		   	&0.6536$\pm$0.0005  &0.6535$\pm$0.0007  &68.73 $\pm$ 0.06  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4828$\pm$0.0017  &0.4809$\pm$0.0024  &79.17 $\pm$ 0.04  &$\times$15.18 \\ \hline
			\textbf{LLC-SAPL}       &0.4378$\pm$0.0012  &0.4359$\pm$0.0013  &80.61 $\pm$ 0.10 &$\times$16.72  \\ \hline
			\textbf{LLC-JO}         &0.4122$\pm$0.0025  &0.4190$\pm$0.0031  & 81.75 $\pm$ 0.11  &$\times$14.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.4045$\pm$0.0037}  &\textbf{0.4095$\pm$0.0040}  &\textbf{81.99 $\pm$ 0.21}   &$\times$14.52\\ \hline
		\caption{Comparison of different algorithms in terms of train loss, test loss, classification accuracy and test time (normalized to test time of SVM)}

>>>>

	\begin{table}
		\begin{tabu} to \textwidth {|X[c]| X[c]| X[c]| X[c]| X[c]|}
			\hline
			phishing              & Train loss & Test loss & Acc(\%) &Test time \\
			\hline
			\textbf{SVM} 		   	&0.1826 &0.1964  & 92.24  & $\times$1  \\ \hline
			\textbf{LLSVM}     		&0.1688  &0.1861  & 92.66  & $\times$8.91 \\ \hline
			\textbf{LLC-SAPL}       &0.1385 &0.1509  & 93.92  & $\times$9.27 \\ \hline
			\textbf{LLC-JO}         &0.0580  &0.1026  & 95.66  & $\times$8.66 \\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0487}  &\textbf{0.0965}  & \textbf{95.84} &$\times$8.91 \\ \hline
			\hline
			Magic04              & Train loss & Test loss & Acc(\%) &Test time \\
			\hline
			\textbf{SVM} 		   	&0.4810 &0.5004  &78.33   &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4022  &0.4289  &79.57   &$\times$21.56 \\ \hline
			\textbf{LLC-SAPL}       &0.3670  &0.3923  &81.60   &$\times$22.04 \\ \hline
			\textbf{LLC-JO}         &0.3025  &0.3339  &84.88  &$\times$22.92\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.2852}  &\textbf{0.3238}  &\textbf{85.14}   &$\times$22.92\\ \hline
			\hline
			IJCNN              & Train loss & Test loss & Acc(\%) &Test time\\
			\hline
			\textbf{SVM} 		   	&0.1827 &0.1863  & 90.50   &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.1081  &0.1130  & 94.51  &$\times$15.52\\ \hline
			\textbf{LLC-SAPL}       &0.1002  &0.1054  & 95.17   &$\times$15.78\\ \hline
			\textbf{LLC-JO}         &0.0703 &0.0683  & 97.66  &$\times$16.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0550}  &\textbf{0.0584}  &\textbf{98.26}   &$\times$15.42\\ \hline
			\hline
			w8a              & Train loss & Test loss & Acc(\%) &Test time\\
			\hline
			\textbf{SVM} 		   	&0.0552 &0.0567  & 97.07  &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.0320 &0.0333  & 98.45  &$\times$11.72\\ \hline
			\textbf{LLC-SAPL}       &0.0262 &0.0274  & 98.74  &$\times$12.78\\ \hline
			\textbf{LLC-JO}         &0.0250  &0.0262  & 98.74  &$\times$10.01\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0213}  &\textbf{0.0228}  &\textbf{98.96}   &$\times$10.28\\ \hline
			\hline
			connect-4              & Train loss & Test loss & Acc(\%) &Test time\\
			\hline
			\textbf{SVM} 		   	&0.4268  &0.4257  & 81.50   &$\times$1\\ \hline
			\textbf{LLSVM}     		&0.2998  &0.3196  & 87.30   &$\times$7.52\\ \hline
			\textbf{LLC-SAPL}       &0.2626  &0.2901  & 88.19   &$\times$8.78\\ \hline
			\textbf{LLC-JO}         &0.2180  &0.2663  & 89.15   &$\times$9.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.1496}  &\textbf{0.2225}  &\textbf{90.94}   &$\times$9.92\\ \hline
			\hline
			Covtype              & Train loss & Test loss & Acc(\%) &Test time\\
			\hline
			\textbf{SVM} 		   	&0.6536 &0.6535 &68.73  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4828  &0.4809  &79.17  &$\times$15.18 \\ \hline
			\textbf{LLC-SAPL}       &0.4378 &0.4359 &80.61 &$\times$16.72  \\ \hline
			\textbf{LLC-JO}         &0.4122 &0.4190  & 81.75  &$\times$14.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.4045}  &\textbf{0.4095}  &\textbf{81.99}   &$\times$14.52\\ \hline
		\end{tabu}
		\caption{Comparison of different algorithms in terms of train loss, test loss, classification accuracy and test time (normalized to test time of SVM)}
	\end{table}
